Empirical Analysis of the Role of Energy in Economic Growth

### 2013-02-02 EconGrowth.Rnw
Formatting for the C-D fit parameters graph.

<<CD_Params_Graph, fig.width=figWidth, fig.height=3.0, fig.cap="Cobb-Douglas (without energy) model parameters.", echo=FALSE>>=
createCDParamsGraph <- function(){
  # Create a data table with the following columns:
  # country abbrev, parameter (lambda, alpha, or beta), -95% CI, value, +95% CI
  dataTable <- do.call("rbind", lapply(countryAbbrevs, cobbDouglasCountryRowsForParamsGraph))

  graph <- segplot(country ~ upperCI + lowerCI | parameter, 
                   data = dataTable, 
                   centers = value, #identifies where the dots should be placed
                   draw.bands = FALSE, #provides nicer error bars
                   horizontal = FALSE, #makes error bars vertical
                   layout = c(3,1), #3 column, 1 row
                   strip = strip.custom(bg="white"), #Sets strip parameters
                   scales=list(cex=scaleTextSize, #controls text size on scales.
                               tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
                               y=list(at=c(0.0, 0.2, 0.4, 0.6, 0.8, 1.0), #tick mark locations on y axis
                                      relation="free")), #allow free relations of axis limits?
                   ylim=list(c(-0.1,0.2), c(-0.5, 1.5), c(-0.5, 1.5)) #y axis limits
                   ) 
  return(graph)
}
createCDParamsGraph()
@

>>>>

<<CD_Params_Graph, fig.width=figWidth, fig.height=3.5, fig.cap="Cobb-Douglas (without energy) model parameters.", echo=FALSE>>=
createCDParamsGraph <- function(){
  # Create a data table with the following columns:
  # country abbrev, parameter (lambda, alpha, or beta), -95% CI, value, +95% CI
  dataTable <- do.call("rbind", lapply(countryAbbrevs, cobbDouglasCountryRowsForParamsGraph))

  graph <- segplot(country ~ upperCI + lowerCI | parameter, 
                   data = dataTable, 
                   centers = value, #identifies where the dots should be placed
                   draw.bands = FALSE, #provides nicer error bars
                   horizontal = FALSE, #makes error bars vertical and puts the countries in the x axis
                   layout = c(3,1), #3 column, 1 row
                   strip = strip.custom(bg="white"), #Sets strip parameters
                   col = "black", #Sets line color to black
                   lwd = 1, #Sets line width to 1.0
                   ylim = list(c(-0.05, 0.1), c(-0.5, 1.5), c(-0.5, 1.5)), #y axis limits
                   scales = list(cex=scaleTextSize, #controls text size on scales.
                                 tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
                                 y=list(relation="free",                        #allow each axis to be different
                                        at=list(c(0.0, 0.05, 0.1),   #tick mark locations on y axis
                                                c(0.0, 0.5, 1.0), 
                                                c(0.0, 0.5, 1.0)
                                                )
                                        )
                                 )
                   )
  return(graph)
}
createCDParamsGraph()
@
